Activity Monitoring
===================

# Loading and preprocessing data.

```{r}
par(mfrow=c(1, 1))

dtx <- read.csv("activity.csv", stringsAsFactors = F)
dtx$DT <- strptime(dtx$date, format="%Y-%m-%d")
dtx$WD <- weekdays(dtx$DT, abbreviate=T)
dx <- dtx[!is.na(dtx$steps),]
```

# Mean(s) of the total number of steps taken per day

```{r fig.width=10, fig.height=8}
dx <- dtx[!is.na(dtx$steps),]
len <- sum(dx$steps)
d0 <- character(length = len)
k <- 1L
for (i in seq(1, nrow(dx))){
    cc <- dx[i,]
    if (cc$steps > 0) {
        for (j in seq(1, cc$steps)) {
            d0[k] <- cc$date
            k <- k + 1L
        }
    }
}
d0 <- strptime(d0, format="%Y-%m-%d")
hist(d0, breaks="days", format="%Y-%m-%d", col = "red", xlab="Date", 
     ylab="Number of Steps", main="Number of Steps (per Day)", freq = TRUE)
```

# Mean(s) and median(s) steps taken per day

```{r}
dx <- dtx[!is.na(dtx$steps),]
d1 <- split(dx, factor(as.Date(dx$date, format="%Y-%m-%d")))
d2 <- data.frame()
for (c in d1) {
    d2 <- rbind(d2, data.frame(Date = c[1, "DT"], Mean = mean(c$steps), Median = median(c$steps)))
}
d2
```

# Average daily activity pattern

```{r fig.width=10, fig.height=8}
dx <- dtx[!is.na(dtx$steps),]
d1 <- split(dx, factor(dx$interval))
d3 <- data.frame()
for (c in d1) {
    d3 <- rbind(d3, data.frame(Interval = c[1, "interval"], Mean = mean(c$steps)))
}

plot(d3$Interval, d3$Mean, type ="l", lwd = 3, col="red", main = "Average Steps for 5 Minute Interval", 
     xlab = "Interval", ylab = "Average steps")


max_steps <- d3[order(d3$Mean,decreasing=T),][1,]
mis_count <- sum(is.na(dtx))
total_count <- nrow(dtx)

```

# Maximum number of step(s) (interval, mean) = `r max_steps`

# Missing count `r  mis_count`

# Total count `r total_count`

# Result(s) of imputing missing values

```{r fig.width=8, fig.height=6}
dx <- dtx[!is.na(dtx$steps),]
dx$key <- paste(dx$interval, dx$WD, sep=";")
d6 <- split(dx, factor(dx$key))
d7 <- data.frame()
for (c in d6) {
    d7 <- rbind(d7, data.frame(key = c[1, "key"], mean = mean(c$steps)))
}

dy <- dtx[is.na(dtx$steps),]
dy$key <- paste(dy$interval, dy$WD, sep=";")
st <- numeric()
for (i in 1:nrow(dy)) {
    cc <- dy[i,]
    st <- c(st, d7[d7$key == paste(cc$interval, cc$WD, sep=";"), "mean"])
}
dy$steps <- st     

dtx1 <- rbind(dx, dy)

dx <- dtx1
len <- sum(dx$steps)
d0 <- character(length = len)
k <- 1L
for (i in seq(1, nrow(dx))){
    cc <- dx[i,]
    if (cc$steps > 0) {
        for (j in seq(1, cc$steps)) {
            d0[k] <- cc$date
            k <- k + 1L
        }
    }
}
d0 <- strptime(d0, format="%Y-%m-%d")
hist(d0, breaks="days", format="%Y-%m-%d", col = "red", xlab="Date", ylab="Steps", main="Steps per Day", freq = TRUE)

```


# Difference in activity patterns between weekdays and weekends

```{r fig.width=8, fig.height=12}
par(mfrow=c(2, 1))

dx <- dtx[!is.na(dtx$steps),]

d0 <- dx[(dx$WD == "вс") | (dx$WD == "сб"), ]

d1 <- split(d0, factor(d0$interval))
d3 <- data.frame()
for (c in d1) {
    d3 <- rbind(d3, data.frame(Interval = c[1, "interval"], Mean = mean(c$steps)))
}
plot(d3$Interval, d3$Mean, type ="l", lwd = 1.5, col="red", main = "Weekend", 
     xlab = "Interval", ylab = "Steps")

d0 <- dx[!((dx$WD == "вс") | (dx$WD == "сб")), ]
d1 <- split(d0, factor(d0$interval))
d3 <- data.frame()
for (c in d1) {
    d3 <- rbind(d3, data.frame(Interval = c[1, "interval"], Mean = mean(c$steps)))
}
plot(d3$Interval, d3$Mean, type ="l", lwd = 1.5, col="red", main = "Weekday", 
     xlab = "Interval", ylab = "Steps")
```


